A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-07 manuscript.Rmd
add summary

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `missing_rcode_simulation` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `missing_rcode_simulation`%.
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.

@@

@@

@@

<!-- maybe we add here the real data? #25 -->

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data <!-- AP: can you add the reference to this tight reproducibility requirements that you told me about?-->. We use containers to guarantee that all code components are available and work as expected. Ideally, all data is also stored in the repository. In practice, however, there are various reasons, which may prohibit you from making your data available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request. <!-- AP please cite the SHARE data and explain as an example what one has to do to ontain these data -->.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

@@

# Archiving and Dissemination

@@

>>>>

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision. <!--AP shouldn't this be in the simulation part?-->
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `missing_rcode_simulation` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `missing_rcode_simulation`%.
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.

@@

### Data Documentation

<!--AP cite WORCS and some arguments for documenting your data. Also, cite the codebook package -->

@@

<!-- AP: this is a nice example but why is this an abstract example now? I thought that 
we walk through one(!) example. I think this really should be the concrete Makefile from
the analysis that we are talking about -->

@@

Note that both this tutorial as well as our article on the reproducible workflow [@Peikert2019] were created using this workflow and can be reproduced from their source code repositories <!--AP add links -->.
<!-- maybe we add here the real data? #25 -->

@@

<!--AP: make sure to cite WORCS and describe what WORCS is proposing here-->
<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data <!-- AP: can you add the reference to this tight reproducibility requirements that you told me about?-->. We use containers to guarantee that all code components are available and work as expected. Ideally, all data is also stored in the repository. In practice, however, there are various reasons, which may prohibit you from making your data available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request. <!-- AP please cite the SHARE data and explain as an example what one has to do to ontain these data -->.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

@@

# Archival and Dissemination

@@

# Summary

Here, we provided a step-by-step tutorial with what we think are best practices for creating a fully reproducible repository for data analysis projects that center on the statistical programming language R. The workflow avoids common threats to reproducibility, such as missing files, missing software dependencies, side-effects through changing dependent software packages, changes in the programming language, or even at the level of the operating system itself. 
<!-- AP: add more. Summarize. Talk about the benefits. Talk about the limitations. What are the threats to reproducibility. Make the case that adopting this workflow is easy and can even be done for existing repositories. Also, wasn't an important point of repro that it itself is not a dependency? I think this needs to be strengthened and probably already said in the intro-->
